### 2018-09-02 sections/signal_background_modeling.tex
more editing

Samples of simulated $\ttbar \to WbHq$ events are generated with the next-to-leading-order (NLO) generator\footnote{In the following, 
the order of a generator should be understood as referring to the order in the strong coupling constant at which the matrix element calculation 
is performed.} {\amcatnlolong}~2.4.3~\cite{Alwall:2014hca}  (referred to in the following as {\amcatnlo}) with the NNPDF3.0 NLO~\cite{Ball:2014uwa} parton distribution function (PDF) set and interfaced to {\pythia} 8.212~\cite{Sjostrand:2007gs} with the NNPDF2.3 LO~\cite{Ball:2012cx} PDF set for the modelling of parton showering, hadronisation, and the underlying event. 
The A14~\cite{ATLASUETune4} set of tuned parameters in {\pythia} controlling the description of multiparton interactions and  
initial and final state radiation, referred to as the ``tune'', is used.
The signal sample is normalised to the same cross section as used for the $t\bar{t}\to WbWb$ sample (see discussion below) and
assuming a reference branching ratio $\BR_{\mathrm{ref}}(t\to Hq)=1\%$.
The case of both top quarks decaying into $Hq$ is neglected in the analysis given existing upper limits on $\BR(t \to Hq)$ (see Section~\ref{sec:intro}).

@@

%The $\Hbb$ search requires a more sophisticated treatment of the $\ttbar$ background. 
The $\ttbar$ background selected by the $\Hbb$ search is enriched in $\ttbar$+heavy-flavour production, and thus requires a more sophisticated 
treatment than provided by the nominal $\ttbar$ sample. 
%The large and complex $\ttbar$ background selected by the $\Hbb$ search requires a more sophisticated treatment than provided by the nominal $\ttbar$ sample. 
Therefore, the simulated $\ttbar$ events are categorised depending 
on the flavour content of additional particle jets not originating from the decay of the $\ttbar$ system (see Ref.~\cite{Aaboud:2017rss} for details).
Events labelled as either \ttbin\ or \ttcin\ are generically referred to in the following as $\ttbar$+HF events, where HF stands for ``heavy flavour''.
The remaining events are labelled as $\ttbar$+light-jets events, including those with no additional jets. 
A finer categorisation of \ttbin\ events is considered for the purpose of applying further corrections and
assigning systematic uncertainties associated with the modelling of heavy-flavour production in different event topologies~\cite{Aaboud:2017rss}.
In particular, the \ttbin\ events are reweighted to an NLO prediction in the four-flavour (4F) scheme 
of \ttbin\ production including parton showering~\cite{Cascioli:2013era}, based on {\ShOLlong}~\cite{Gleisberg:2008ta, Cascioli:2011va} (referred to as {\ShOL} 
in the following) using the CT10 PDF set.  This reweighting is performed in such a way that the inter-normalisations of the \ttbin\ categories are at NLO accuracy, 
while preserving the nominal \ttbin\ cross section of the nominal $\ttbar$ sample. This reweighting is applied to the alternative $\ttbar$ samples as well.

>>>>

Samples of simulated $\ttbar \to WbHq$ events are generated with the next-to-leading-order (NLO) generator\footnote{In the following, 
the order of a generator should be understood as referring to the order in the strong coupling constant at which the matrix element calculation 
is performed.} {\amcatnlolong}~2.4.3~\cite{Alwall:2014hca}  (referred to in the following as {\amcatnlo}) with the NNPDF3.0 NLO~\cite{Ball:2014uwa} parton distribution function (PDF) set and interfaced to {\pythia} 8.212~\cite{Sjostrand:2007gs} with the NNPDF2.3 LO~\cite{Ball:2012cx} PDF set for the modelling of parton showering, hadronisation, and the underlying event. 
The A14~\cite{ATLASUETune4} set of tuned parameters in {\pythia} controlling the description of multiparton interactions and  
initial and final state radiation, referred to as the ``tune'', is used.
The signal sample is normalised to the same total cross section as used for the $t\bar{t}\to WbWb$ sample (see discussion below) and
assuming a reference branching ratio $\BR_{\mathrm{ref}}(t\to Hq)=1\%$.
The case of both top quarks decaying into $Hq$ is neglected in the analysis given existing upper limits on $\BR(t \to Hq)$ (see Section~\ref{sec:intro}).

@@

%The $\Hbb$ search requires a more sophisticated treatment of the $\ttbar$ background. 
The $\ttbar$ background selected by the $\Hbb$ search is enriched in $\ttbar$+heavy-flavour production, and thus requires a more sophisticated 
treatment than provided by the nominal $\ttbar$ sample. 
%The large and complex $\ttbar$ background selected by the $\Hbb$ search requires a more sophisticated treatment than provided by the nominal $\ttbar$ sample. 
Therefore, the simulated $\ttbar$ events are categorised depending 
on the flavour content of additional particle jets not originating from the decay of the $\ttbar$ system (see Ref.~\cite{Aaboud:2017rss} for details).
Events labelled as either \ttbin\ or \ttcin\ are generically referred to in the following as $\ttbar$+HF events, where HF stands for ``heavy flavour''.
The remaining events are labelled as $\ttbar$+light-jets events, including those with no additional jets. 
A finer categorisation of \ttbin\ events is considered for the purpose of applying further corrections and
assigning systematic uncertainties associated with the modelling of heavy-flavour production in different event topologies~\cite{Aaboud:2017rss}.
In particular, the \ttbin\ events are reweighted to an NLO prediction in the four-flavour (4F) scheme 
of \ttbin\ production including parton showering~\cite{Cascioli:2013era}, based on {\ShOLlong}~\cite{Gleisberg:2008ta, Cascioli:2011va} (referred to as {\ShOL} 
in the following) using the CT10 PDF set.  This reweighting is performed in such a way that the inter-normalisations of the \ttbin\ categories are at NLO accuracy, 
while preserving the nominal \ttbin\ cross section of the nominal $\ttbar$ sample. 
%This reweighting is applied to the alternative $\ttbar$ samples as well.
This reweighting is also applied to the alternative $\ttbar$ samples that are used to study systematic uncertainties (see section~\ref{sec:syst_bkgmodeling}).
